\documentclass{article}

\usepackage[margin=1in]{geometry}

\title{Elevated MacBook Access Contract}
\author{Falls Church City Public Schools}

\begin{document}
\maketitle
\noindent\textbf{Please read this contract in its entirety. Its stipulations are personally relevant to your use of FCCPS MacBooks.}

GMHS provides elevated computer access to students with advanced understanding of computer science and a need for deeper control of their FCCPS-issued devices.

All students seeking elevated use privileges must consent to the terms of this agreement.

By signing below, I recognize that:
Rights to using my FCCPS-issued MacBook, both with and without Elevated Use, is a privilege and not a right. FCCPS provides me with a personal device for my own personal education and is not obligated to allow me to do anything I desire with it.
I am bound by personal integrity as well as this legally binding contract to remain within the limits of FCCPS’ Acceptable Use Policy and other relevant school policies.
Having Elevated Access may enable tampering with MacBook systems in a way which would typically be difficult. Having elevated access specifically does not give students a right to damage FCCPS software.
Trust is being invested in me to not violate FCCPS Policy Section 9.40 (FCCPS INTERNET SAFETY AND ACCEPTABLE USE OF ELECTRONIC MEDIA).

Furthermore, I promise that:
I will not use my elevated access to damage any FCCPS systems or to remove or tamper with any preinstalled software. Specifically, I will not interfere in any way with any systems used by GMHS to monitor my computer.
All actions I take using root access will be without malicious intent. I will never attempt to subvert the authority of the GMHS IT department, and will leave open all standard means of supervision.
I will not install software packages, knowingly or otherwise, designed to perform any malicious process.
All purposes pursued using elevated access privileges will be strictly for the benefit of my own education.

Violation of any of these terms may result in revocation of Elevated Use or of MacBook use privileges outright.

Student signature: \underline{\hspace{3cm}} Date: \underline{\hspace{2cm}}
Parent signature:  \underline{\hspace{3cm}} Date: \underline{\hspace{2cm}}
\end{document}
