\documentclass{article}

\usepackage[margin=1in]{geometry}

\pagenumbering{gobble}

\title{Elevated MacBook Access Contract}
\author{Falls Church City Public Schools}

\begin{document}
\maketitle
\noindent\textbf{Please read this contract in its entirety. Its stipulations are personally relevant to your use of FCCPS MacBooks.}

GMHS provides elevated computer access to students with advanced understanding of computer science and a need for deeper control of their FCCPS-issued devices.

All students seeking elevated use privileges must consent to the terms of this agreement.

By signing below, I recognize that:
\begin{itemize}
\item{Rights to using my FCCPS-issued MacBook, both with and without Elevated Use, is a privilege and not a right. FCCPS provides me with a personal device for my own personal education and is not obligated to allow me to do anything I desire with it.}
\item{I am bound by personal integrity as well as this legally binding contract to remain within the limits of FCCPS’ Acceptable Use Policy and other relevant school policies.}
\item{Having Elevated Access may enable tampering with MacBook systems in a way which would typically be difficult. Having elevated access specifically does not give students a right to damage FCCPS software.}
\item{Trust is being invested in me to not violate FCCPS Policy Section 9.40 (FCCPS INTERNET SAFETY AND ACCEPTABLE USE OF ELECTRONIC MEDIA).}
\end{itemize}

Furthermore, I promise that:
\begin{itemize}
\item{I will not use my elevated access to damage any FCCPS systems or to remove or tamper with any preinstalled software. Specifically, I will not interfere in any way with any systems used by GMHS to monitor my computer.}
\item{All actions I take using root access will be without malicious intent. I will never attempt to subvert the authority of the GMHS IT department, and will leave open all standard means of supervision.}
\item{I will not install software packages, knowingly or otherwise, designed to perform any malicious process.}
\item{All purposes pursued using elevated access privileges will be strictly for the benefit of my own education.}
\end{itemize}

Violation of any of these terms may result in revocation of Elevated Access or of MacBook use privileges outright.

\vspace{1cm}
\noindent
Student signature: \underline{\hspace{3cm}} Date: \underline{\hspace{2cm}}\\
\noindent
Parent signature:  \underline{\hspace{3cm}} Date: \underline{\hspace{2cm}}
\end{document}
